Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-03 paper.tex
added a reference about the Linux kernel
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro, Fischer, and Marques-Silva was further developed to verify correct lock acquisition ordering and the absence of deadlocks, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira17}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state-space exploration~\cite{Inverso14,civl15}; however, the classes of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores~\cite{Grumberg05}, with the goal to remove redundant behaviour or analyze interpolants~\cite{McMillan11} to prove non-interference of context switches.

>>>>

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro, Fischer, and Marques-Silva was further developed to verify correct lock acquisition ordering and the absence of deadlocks, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira17}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state-space exploration~\cite{Inverso14,civl15}, and also extensions to verify the Debian GNU/Linux distribution based on a context- and thread-sensitive abstract interpretation framework~\cite{DBLP:conf/kbse/KroeningPSW16}; however, the classes of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores~\cite{Grumberg05}, with the goal to remove redundant behaviour or analyze interpolants~\cite{McMillan11} to prove non-interference of context switches.
